Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-19 chi2012.tex
a  few more

The second finding is that equivalent properties were sometimes, though only rarely, given the same name.  Thus, terminological heterogeneity was prevalent across data records we observed.  Structural heterogeneity, however, was comparatively rare, with the most common case being similar to the birthday example above; a leaf property on one record modeled as a subtree in the other.  We also encountered, particularly in the Weather category, examples of fields which had data nested in textual description fields, which hints their intended use in RSS and other feed readers than as stuctured data feeds.

@@

Although not included in the table above, we also examined the consistency in enumerated type ranges across data sources above.  Ranges of enumerated types for properties as seemingly simple as ``Gender'' disagreed among social networks; while Facebook allowed only ``Male'' and ``Female'' for values, Google+ included a third option,``other''.  ``Relationship status'' was another for which a majority of the values had correspondences between platforms but there wer a number of unique values not present in the rest.

>>>>

The second finding is that equivalent properties were sometimes, though only rarely, given the same name.  Thus, terminological heterogeneity was prevalent across data records we observed.  Structural heterogeneity, however, was comparatively rare, with the most common case being similar to the birthday example above; a leaf property on one record modeled as a subtree in the other.  We also encountered only 2 examples of fields which had data nested in textual description fields, both from records in the Weather category, which hints their intended use in RSS and other feed readers than as stuctured data feeds.

@@

Although not included in the table above, we also examined the ranges of enumerated type values across data sources.  There was substantial terminological heterogeneity among such values, but also many cases where one source had additional values not supported in the range of the other.  For example, the property ``Gender''  on Facebook allowed only ``Male'' and ``Female'' for values, while Google+ included a third option,``other''.  ``Relationship status'' was another which was similarly complex. Amazon's
